FATE summary results

### 2019-09-04 paper draft.Rmd
Updating GOA biology plots

```{r, echo=F}
GOA.biol <- readRDS("/Users/MikeLitzow/Documents/R/Fate/fate-ewi/GOA_biol_5.15.18.rds") 
GOA.biol$summary
```

@@

# limit to GOA
GOA <- ewidata[ewidata$system %in% c("WGOA", "EGOA"),]

# drop CI pinks as they aren't present in odd and even years
GOA <- filter(GOA, code != "CI.PI")

# drop dogfish (too many NAs)
drop <- grep("DOGF", GOA$code)
GOA <- GOA[-drop,]

# drop birds and icy strait and chatnam and seward line and CPR
drop <- c(grep("PROD.", GOA$code), grep("PHEN.", GOA$code), grep("ICY", GOA$code), grep("CHAT", GOA$code), grep("SEWARD", GOA$code), 
          grep("mesozoo", GOA$code), grep("diatoms", GOA$code), grep("copepod", GOA$code))
GOA <- GOA[-drop,]

# and start in 1972
GOA <- GOA[GOA$year>=1972,]

# herring time series are repeats, remove
drop <- grep("SE.HER.ROE", GOA$code)
GOA <- GOA[-drop,]

# and drop the ichthyo data
drop <- grep("ICH", GOA$code)
GOA <- GOA[-drop,]

@@

new.names <- c("Chignik.coho", "Chignik.pink", "Chiniak.eulachon", "Chiniak.jellyfish", "Chiniak.shrimp", "Cook.Inlet.coho", "Kodiak.coho", "Kodiak.pink", "Pavlof.capelin", "Pavlof.eulachon", "Pavlof.jellyfish", "Pavlof.shrimp", "Prince.William.coho", "Prince.William.pink", "Southeast.coho", "Southeast.herring", "Southeast.pink", "South.Peninsula.coho", "South.Peninsula.pink")

>>>>

```{r, echo=F}
GOA.biol <- readRDS("GOA_biol_9.4.19.rds") 
GOA.biol$summary
```

@@

# reload the version of data used
GOA <- read.csv("updated GOA biology data.csv")

@@

new.names <- c("Chignik.coho", "Chignik.pink", "Chiniak.eulachon", "Chiniak.jellyfish", "Chiniak.shrimp", "Cook.Inlet.coho", "Kodiak.coho", "Kodiak.pink", "Pavlof.capelin", "Pavlof.eulachon", "Pavlof.jellyfish", "Pavlof.shrimp", "Prince.William.coho", "Southeast.coho", "Southeast.herring", "Southeast.pink", "South.Peninsula.coho", "South.Peninsula.pink")
